\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2019-12-08 analysis/paper/paper.tex
fix table captions

\hypertarget{code-formatting}{%
\section{Code formatting}\label{code-formatting}}

Don't use markdown, instead use the more precise latex commands:

\begin{itemize}
\item
  \proglang{Java}
\item
  \pkg{plyr}
\item
  \code{print("abc")}
\end{itemize}

@@

hazard ratios 2. If, however, the absolute risks are of interest, they
have to be recovered using the semi-parametric Breslow estimator 3.
Alternative approaches for fitting flexible hazard models for estimating
absolute risks, not requiring this two-step approach? Yes!
\citep{hanley2009fitting}

@@

These packages can belong to three main categories: non-proportional
hazards, regularization and competing risks. Besides these three main
categories, there are extra features of interest as well. Table XXX
summarizes the findings.

Many packages exist that implement semi-parametric cox models. Of those,
glmnet \citeyearpar{regpathcox}???, glmpath \citeyearpar{park_hastie},
penalized \citeyearpar{l1penal}, RiskRegression
\citeyearpar{gerds_blanche} introduce penalization in their model
fitting. CoxRidge \citeyearpar{perperoglou} , rstpm2
\citeyearpar{clements_liu} and survival \citeyearpar{survival-package}
include penalization, but they implement the extended cox model
permitting intuitive non proportional hazard modeling while the previous
four do not. In terms of penalization, the benefit of casebase comes
from its flexibility. Linear models have a wide tool set, considerably
larger than those made for cox regression (\emph{reference for number of
packages between their task views, regression is spread out across
Multivariate, SocialSciences, Robust among others. The focus of this
task view is on Optimization Infrastructure Packages , General Purpose
Continuous Solvers , Mathematical Programming Solvers , and Specific
Applications in Optimization , or Multi Objective Optimization}).
Casebase permits many regularization tools developed for linear
regression to be repurposed within a survival context.

Parametric models permit non-proportional hazards and are implemented in
a handful of packages. Of interest are CFC
\citeyearpar{sharabiani_mahani_2019}, flexsurv \citeyearpar{flexsurv} ,
SmoothHazard \citeyearpar{smoothHazard}, Rsptm2
\citeyearpar{clements_liu} and Survival \citeyearpar{survival-package}.
Smooth hazard is limited to weibull
distributions\citeyearpar{smoothHazard}, where as flexsurv and survival
contain implementations for users to supply any distribution they would
like \citeyearpar{survival-package}, \citeyearpar{flexsurv}. Flexsurv,
smooth hazard, mets and rstpm2 can use splines, permitting a flexible
fit over time \citeyearpar{flexsurv}, \citeyearpar{smoothHazard},
\citeyearpar{scheike2014estimating}, \citeyearpar{clements_liu} . Though
casebase is limited to 3 distributions at the moment, it also uses
splines allowing for distributions that may not be consistent over
survival time.

Of the methods mentioned so far, only CFC,flexsurv, mets and survival
contain implementations for competing risks
\citeyearpar{sharabiani_mahani_2019},
\citeyearpar{flexsurv},\citeyearpar{scheike2014estimating}
,\citeyearpar{survival-package} (\emph{how is it done for parametric
models?}). The differentiating factor between these packages and
casebase is that casebase handles competing risks through multiple
logistic regression. Smooth hazard, survival and Rstpm2 can handle
interval censoring, where as casebase currently can not. Interval
censoring is simple feature to implement and is a potential improvement
to add to casebase. (There's also multistate models, which I haven't
mentioned in this paper)

Of all the packages listed in the table, CFC , Flexsurv, mets,
RiskRegression, rstpm2 and survival have implementations for cumulative
incidence \citeyearpar{sharabiani_mahani_2019}, \citeyearpar{flexsurv},
\citeyearpar{scheike2014estimating}, \citeyearpar{gerds_blanche},
\citeyearpar{clements_liu}, \citeyearpar{survival-package}. Since
casebase is parametric, the baseline hazard is known and requires
integration to retrieve the cumulative incidence. This is similar to the
approaches of CFC and flexsurv \citeyearpar{sharabiani_mahani_2019},
\citeyearpar{flexsurv}, while the other packages use semi-parametric
approaches to retrieve the baseline after fitting
\citeyearpar{scheike2014estimating}, \citeyearpar{gerds_blanche}. rstpm2
and survival use both for their respective parametric and
semi-parametric model implementations \citeyearpar{clements_liu},
\citeyearpar{survival-package}.

\begin{table}[]

@@

We examined the Study to Understand Prognoses Preferences Outcomes and
Risks of Treatment (SUPPORT) dataset (REF from main site). the SUPPORT
dataset tracks death for individuals who are considered seriously ill
within a hospital. Imputation was conducted using the default methods in
the mice package in R, available on CRAN. Before imputation, there was a
total of 1000 individuals and 35 variables. After imputation, we have
474 observations where 67.5\% of individuals in the study experience the
event of interest. The SUPPORT dataset will be used to demonstrate
regularization within casebase (REF), while comparing their absolute
risk preditions for a new individual. A description of each variable can
be found in table XXX1 and a breakdown of each categorical variable in
table XXX2. The data was downloaded from the main author's website, and
it is also available as part of the casebase package.

\begin{table}[]

@@

This report was generated on 2019-12-06 16:16:07 using the following
computational environment and dependencies:

@@

#>  version  R version 3.6.0 (2019-04-26)
#>  os       macOS High Sierra 10.13.6   
#>  system   x86_64, darwin15.6.0        

@@

#>  tz       America/Montreal            
#>  date     2019-12-06                  

@@

#> - Packages -------------------------------------------------------------------
#>  package     * version    date       lib
#>  assertthat    0.2.1      2019-03-21 [1]
#>  backports     1.1.5      2019-10-02 [1]
#>  broom         0.5.2      2019-04-07 [1]
#>  callr         3.3.2      2019-09-22 [1]
#>  casebase    * 0.2.1.9001 2019-08-20 [1]
#>  cellranger    1.1.0      2016-07-27 [1]
#>  cli           1.1.0      2019-03-19 [1]
#>  codetools     0.2-16     2018-12-24 [1]
#>  colorspace    1.4-1      2019-03-18 [1]
#>  crayon        1.3.4      2017-09-16 [1]
#>  data.table    1.12.6     2019-10-18 [1]
#>  DBI           1.0.0      2018-05-02 [1]
#>  dbplyr        1.4.2      2019-06-17 [1]
#>  desc          1.2.0      2018-05-01 [1]
#>  devtools      2.2.1      2019-09-24 [1]
#>  digest        0.6.23     2019-11-23 [1]
#>  dplyr       * 0.8.3      2019-07-04 [1]
#>  ellipsis      0.3.0      2019-09-20 [1]
#>  evaluate      0.14       2019-05-28 [1]
#>  forcats     * 0.4.0      2019-02-17 [1]
#>  foreach       1.4.7      2019-07-27 [1]
#>  fs            1.3.1      2019-05-06 [1]
#>  generics      0.0.2      2018-11-29 [1]
#>  ggplot2     * 3.2.1      2019-08-10 [1]
#>  glmnet      * 3.0-1      2019-11-15 [1]
#>  glue          1.3.1      2019-03-12 [1]
#>  gtable        0.3.0      2019-03-25 [1]
#>  haven         2.2.0      2019-11-08 [1]
#>  hms           0.5.2      2019-10-30 [1]
#>  htmltools     0.4.0      2019-10-04 [1]
#>  httr          1.4.1      2019-08-05 [1]
#>  iterators     1.0.12     2019-07-26 [1]
#>  jsonlite      1.6        2018-12-07 [1]
#>  knitr         1.26       2019-11-12 [1]
#>  lattice       0.20-38    2018-11-04 [1]
#>  lazyeval      0.2.2      2019-03-15 [1]
#>  lifecycle     0.1.0      2019-08-01 [1]
#>  lubridate     1.7.4      2018-04-11 [1]
#>  magrittr    * 1.5        2014-11-22 [1]
#>  Matrix      * 1.2-17     2019-03-22 [1]
#>  memoise       1.1.0      2017-04-21 [1]
#>  mgcv          1.8-31     2019-11-09 [1]
#>  modelr        0.1.5      2019-08-08 [1]
#>  munsell       0.5.0      2018-06-12 [1]
#>  nlme          3.1-142    2019-11-07 [1]
#>  pillar        1.4.2      2019-06-29 [1]
#>  pkgbuild      1.0.6      2019-10-09 [1]
#>  pkgconfig     2.0.3      2019-09-22 [1]
#>  pkgload       1.0.2      2018-10-29 [1]
#>  prettyunits   1.0.2      2015-07-13 [1]
#>  processx      3.4.1      2019-07-18 [1]
#>  ps            1.3.0      2018-12-21 [1]
#>  purrr       * 0.3.3      2019-10-18 [1]
#>  R6            2.4.1      2019-11-12 [1]
#>  Rcpp          1.0.3      2019-11-08 [1]
#>  readr       * 1.3.1      2018-12-21 [1]
#>  readxl        1.3.1      2019-03-13 [1]
#>  remotes       2.1.0      2019-06-24 [1]
#>  reprex        0.3.0      2019-05-16 [1]
#>  rlang         0.4.2      2019-11-23 [1]
#>  rmarkdown     1.17       2019-11-13 [1]
#>  rprojroot     1.3-2      2018-01-03 [1]
#>  rstudioapi    0.10       2019-03-19 [1]
#>  rticles       0.12       2019-11-12 [1]
#>  rvest         0.3.5      2019-11-08 [1]
#>  scales        1.1.0      2019-11-18 [1]
#>  sessioninfo   1.1.1      2018-11-05 [1]
#>  shape         1.4.4      2018-02-07 [1]
#>  stringi       1.4.3      2019-03-12 [1]
#>  stringr     * 1.4.0      2019-02-10 [1]
#>  survival    * 3.1-7      2019-11-09 [1]
#>  testthat      2.3.0      2019-11-05 [1]
#>  tibble      * 2.1.3      2019-06-06 [1]
#>  tidyr       * 1.0.0      2019-09-11 [1]
#>  tidyselect    0.2.5      2018-10-11 [1]
#>  tidyverse   * 1.3.0      2019-11-21 [1]
#>  usethis       1.5.1      2019-07-04 [1]
#>  vctrs         0.2.0      2019-07-05 [1]
#>  VGAM          1.1-2      2019-11-21 [1]
#>  withr         2.1.2      2018-03-15 [1]
#>  xfun          0.11       2019-11-12 [1]
#>  xml2          1.2.2      2019-08-09 [1]
#>  yaml          2.2.0      2018-07-25 [1]
#>  zeallot       0.1.0      2018-01-28 [1]
#>  source                                  
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  Github (sahirbhatnagar/casebase@aecb816)
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          
#>  CRAN (R 3.6.0)                          

@@

#> [1] /Library/Frameworks/R.framework/Versions/3.6/Resources/library

@@

\begin{CodeOutput}
#> Local:    master /Users/jislam/Desktop/Gits/cbpaper
#> Remote:   master @ origin (https://github.com/Jesse-Islam/cbpaper.git)
#> Head:     [22bfed0] 2019-12-06: currentDraftEdits
\end{CodeOutput}
\end{CodeChunk}

>>>>

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  hazard ratios
\item
  If, however, the absolute risks are of interest, they have to be
  recovered using the semi-parametric Breslow estimator
\item
  Alternative approaches for fitting flexible hazard models for
  estimating absolute risks, not requiring this two-step approach? Yes!
  \citep{hanley2009fitting}
\end{enumerate}

@@

These packages can belong to three main categories: non-proportional
hazards, regularization and competing risks. Besides these three main
categories, there are extra features of interest as well. Table
\ref{tab:surv-pkgs} summarizes the findings.

Many packages exist that implement semi-parametric Cox models. Of those,
\pkg{glmnet} \citeyearpar{regpathcox}???, \pkg{glmpath}
\citeyearpar{park_hastie}, \pkg{penalized} \citeyearpar{l1penal},
\pkg{RiskRegression} \citeyearpar{gerds_blanche} introduce penalization
in their model fitting. \pkg{CoxRidge} \citeyearpar{perperoglou},
\pkg{rstpm2} \citeyearpar{clements_liu} and \pkg{survival}
\citeyearpar{survival-package} include penalization, but they implement
the extended cox model permitting intuitive non proportional hazard
modeling while the previous four do not. In terms of penalization, the
benefits of \pkg{casebase} comes from its flexibility. Linear models
have a wide tool set, considerably larger than those made for Cox
regression. \pkg{casebase} permits many regularization tools developed
for linear regression to be repurposed within a survival context.

Parametric models permit non-proportional hazards and are implemented in
a handful of packages. Of interest are \pkg{CFC}
\citeyearpar{sharabiani_mahani_2019}, \pkg{flexsurv}
\citeyearpar{flexsurv}, \pkg{SmoothHazard} \citeyearpar{smoothHazard},
\pkg{rsptm2} \citeyearpar{clements_liu} and \pkg{survival}
\citeyearpar{survival-package}. \pkg{SmoothHazard} is limited to Weibull
distributions \citeyearpar{smoothHazard}, whereas \pkg{flexsurv} and
\pkg{survival} contain implementations for users to supply any
distribution they would like \citeyearpar{survival-package},
\citeyearpar{flexsurv}. \pkg{flexsurv}, \pkg{smoothhazard}, \pkg{mets}
and \pkg{rstpm2} can use splines, permitting a flexible fit over time
\citeyearpar{flexsurv}, \citeyearpar{smoothHazard},
\citeyearpar{scheike2014estimating}, \citeyearpar{clements_liu}. Though
\pkg{casebase} is limited to three distributions at the moment, it also
uses splines allowing for distributions that may not be consistent over
survival time.

Of the methods mentioned so far, only \pkg{CFC}, \pkg{flexsurv},
\pkg{mets} and \pkg{survival} contain implementations for competing
risks \citeyearpar{sharabiani_mahani_2019}, \citeyearpar{flexsurv},
\citeyearpar{scheike2014estimating}, \citeyearpar{survival-package}. The
differentiating factor between these packages and \pkg{casebase} is that
\pkg{casebase} handles competing risks through multiple logistic
regression. \pkg{SmoothHazard}, \pkg{survival} and \pkg{Rstpm2} can
handle interval censoring, whereas \pkg{casebase} currently cannot.
Interval censoring is a simple feature to implement and is a potential
improvement to add to \pkg{casebase}.

Of all the packages listed in Table \ref{tab:surv-pkgs}, \pkg{CFC},
\pkg{Flexsurv}, \pkg{mets}, \pkg{RiskRegression}, \pkg{rstpm2} and
\pkg{survival} have implementations for cumulative incidence
\citeyearpar{sharabiani_mahani_2019}, \citeyearpar{flexsurv},
\citeyearpar{scheike2014estimating}, \citeyearpar{gerds_blanche},
\citeyearpar{clements_liu}, \citeyearpar{survival-package}. Since
\pkg{casebase} is parametric, the baseline hazard is known and requires
integration to retrieve the cumulative incidence. This is similar to the
approaches of \pkg{CFC} and \pkg{flexsurv}
\citeyearpar{sharabiani_mahani_2019}, \citeyearpar{flexsurv}, while the
other packages use semi-parametric approaches to retrieve the baseline
after fitting \citeyearpar{scheike2014estimating},
\citeyearpar{gerds_blanche}. \pkg{rstpm2} and \pkg{survival} use both
for their respective parametric and semi-parametric model
implementations \citeyearpar{clements_liu},
\citeyearpar{survival-package}.

\begin{table}[ht]

@@

We examined the Study to Understand Prognoses Preferences Outcomes and
Risks of Treatment (SUPPORT) dataset (REF from main site). the SUPPORT
dataset tracks death for individuals who are considered seriously ill
within a hospital. Imputation was conducted using the default methods in
the mice package in R, available on CRAN. Before imputation, there was a
total of 1000 individuals and 35 variables. After imputation, we have
474 observations where 67.5\% of individuals in the study experience the
event of interest. The SUPPORT dataset will be used to demonstrate
regularization within casebase (REF), while comparing their absolute
risk preditions for a new individual. A description of each variable can
be found in Table\textasciitilde{}\ref{tab:support1} and a breakdown of
each categorical variable in Table\textasciitilde{}\ref{tab:support2}.
The data was downloaded from the main author's website, and it is also
available as part of the casebase package.

\begin{table}[ht]

@@

This report was generated on 2019-12-08 12:21:42 using the following
computational environment and dependencies:

@@

#>  version  R version 3.6.1 (2019-07-05)
#>  os       Ubuntu 18.04.3 LTS          
#>  system   x86_64, linux-gnu           

@@

#>  tz       America/Winnipeg            
#>  date     2019-12-08                  

@@

#> - Packages --------------------------------------------------------------
#>  package     * version    date       lib source                          
#>  assertthat    0.2.1      2019-03-21 [1] CRAN (R 3.6.1)                  
#>  backports     1.1.5      2019-10-02 [1] CRAN (R 3.6.1)                  
#>  broom         0.5.2      2019-04-07 [1] CRAN (R 3.6.1)                  
#>  callr         3.3.1      2019-07-18 [1] CRAN (R 3.6.1)                  
#>  casebase    * 0.2.1.9001 2019-07-29 [1] local                           
#>  cellranger    1.1.0      2016-07-27 [1] CRAN (R 3.5.0)                  
#>  cli           1.1.0      2019-03-19 [1] CRAN (R 3.6.1)                  
#>  codetools     0.2-16     2018-12-24 [4] CRAN (R 3.5.2)                  
#>  colorspace    1.4-1      2019-03-18 [1] CRAN (R 3.6.1)                  
#>  crayon        1.3.4      2017-09-16 [1] CRAN (R 3.5.0)                  
#>  data.table    1.12.2     2019-04-07 [1] CRAN (R 3.6.1)                  
#>  desc          1.2.0      2018-05-01 [1] CRAN (R 3.5.0)                  
#>  devtools      2.1.0      2019-07-06 [1] CRAN (R 3.6.1)                  
#>  digest        0.6.22     2019-10-21 [1] CRAN (R 3.6.1)                  
#>  dplyr       * 0.8.3      2019-07-04 [1] CRAN (R 3.6.1)                  
#>  evaluate      0.14       2019-05-28 [1] CRAN (R 3.6.1)                  
#>  forcats     * 0.4.0      2019-02-17 [1] CRAN (R 3.6.1)                  
#>  foreach     * 1.4.4      2017-12-12 [1] CRAN (R 3.5.0)                  
#>  fs            1.3.1      2019-05-06 [1] CRAN (R 3.6.1)                  
#>  generics      0.0.2      2018-11-29 [1] CRAN (R 3.6.1)                  
#>  ggplot2     * 3.2.1      2019-08-10 [1] CRAN (R 3.6.1)                  
#>  glmnet      * 2.0-18     2019-05-20 [1] CRAN (R 3.6.1)                  
#>  glue          1.3.1      2019-03-12 [1] CRAN (R 3.6.1)                  
#>  gtable        0.3.0      2019-03-25 [1] CRAN (R 3.6.1)                  
#>  haven         2.1.1      2019-07-04 [1] CRAN (R 3.6.1)                  
#>  hms           0.5.2      2019-10-30 [1] CRAN (R 3.6.1)                  
#>  htmltools     0.3.6      2017-04-28 [1] CRAN (R 3.5.0)                  
#>  httr          1.4.1      2019-08-05 [1] CRAN (R 3.6.1)                  
#>  iterators     1.0.9      2017-12-12 [1] CRAN (R 3.5.0)                  
#>  jsonlite      1.6        2018-12-07 [1] CRAN (R 3.6.1)                  
#>  knitr         1.23       2019-05-18 [1] CRAN (R 3.6.1)                  
#>  lattice       0.20-38    2018-11-04 [4] CRAN (R 3.5.1)                  
#>  lazyeval      0.2.2      2019-03-15 [1] CRAN (R 3.6.1)                  
#>  lifecycle     0.1.0      2019-08-01 [1] CRAN (R 3.6.1)                  
#>  lubridate     1.7.4      2018-04-11 [1] CRAN (R 3.5.0)                  
#>  magrittr    * 1.5        2014-11-22 [1] CRAN (R 3.5.0)                  
#>  Matrix      * 1.2-18     2019-11-27 [4] CRAN (R 3.6.1)                  
#>  memoise       1.1.0      2017-04-21 [1] CRAN (R 3.5.0)                  
#>  mgcv          1.8-24     2018-06-18 [1] CRAN (R 3.5.1)                  
#>  modelr        0.1.5      2019-08-08 [1] CRAN (R 3.6.1)                  
#>  munsell       0.5.0      2018-06-12 [1] CRAN (R 3.6.1)                  
#>  nlme          3.1-142    2019-11-07 [4] CRAN (R 3.6.1)                  
#>  pillar        1.4.2      2019-06-29 [1] CRAN (R 3.6.1)                  
#>  pkgbuild      1.0.3      2019-03-20 [1] CRAN (R 3.6.1)                  
#>  pkgconfig     2.0.3      2019-09-22 [1] CRAN (R 3.6.1)                  
#>  pkgload       1.0.2      2018-10-29 [1] CRAN (R 3.6.1)                  
#>  prettyunits   1.0.2      2015-07-13 [1] CRAN (R 3.5.2)                  
#>  processx      3.4.1      2019-07-18 [1] CRAN (R 3.6.1)                  
#>  ps            1.3.0      2018-12-21 [1] CRAN (R 3.6.1)                  
#>  purrr       * 0.3.3      2019-10-18 [1] CRAN (R 3.6.1)                  
#>  R6            2.4.1      2019-11-12 [1] CRAN (R 3.6.1)                  
#>  Rcpp          1.0.3      2019-11-08 [1] CRAN (R 3.6.1)                  
#>  readr       * 1.3.1      2018-12-21 [1] CRAN (R 3.6.1)                  
#>  readxl        1.3.1      2019-03-13 [1] CRAN (R 3.6.1)                  
#>  remotes       2.1.0      2019-06-24 [1] CRAN (R 3.6.1)                  
#>  rlang         0.4.1      2019-10-24 [1] CRAN (R 3.6.1)                  
#>  rmarkdown     1.16       2019-10-01 [1] CRAN (R 3.6.1)                  
#>  rprojroot     1.3-2      2018-01-03 [1] CRAN (R 3.5.0)                  
#>  rstudioapi    0.10       2019-03-19 [1] CRAN (R 3.6.1)                  
#>  rticles       0.9.1      2019-07-22 [1] Github (rstudio/rticles@8d56fc6)
#>  rvest         0.3.5      2019-11-08 [1] CRAN (R 3.6.1)                  
#>  scales        1.0.0      2018-08-09 [1] CRAN (R 3.6.1)                  
#>  sessioninfo   1.1.1      2018-11-05 [1] CRAN (R 3.6.1)                  
#>  stringi       1.4.3      2019-03-12 [1] CRAN (R 3.6.1)                  
#>  stringr     * 1.4.0      2019-02-10 [1] CRAN (R 3.6.1)                  
#>  survival    * 2.44-1.1   2019-04-01 [4] CRAN (R 3.6.1)                  
#>  testthat      2.2.0      2019-07-22 [1] CRAN (R 3.6.1)                  
#>  tibble      * 2.1.3      2019-06-06 [1] CRAN (R 3.6.1)                  
#>  tidyr       * 1.0.0      2019-09-11 [1] CRAN (R 3.6.1)                  
#>  tidyselect    0.2.5      2018-10-11 [1] CRAN (R 3.5.2)                  
#>  tidyverse   * 1.2.1      2017-11-14 [1] CRAN (R 3.5.0)                  
#>  usethis       1.5.1      2019-07-04 [1] CRAN (R 3.6.1)                  
#>  vctrs         0.2.0      2019-07-05 [1] CRAN (R 3.6.1)                  
#>  VGAM          1.1-1      2019-02-18 [1] CRAN (R 3.6.1)                  
#>  withr         2.1.2      2018-03-15 [1] CRAN (R 3.5.0)                  
#>  xfun          0.8        2019-06-25 [1] CRAN (R 3.6.1)                  
#>  xml2          1.2.2      2019-08-09 [1] CRAN (R 3.6.1)                  
#>  yaml          2.2.0      2018-07-25 [1] CRAN (R 3.6.1)                  
#>  zeallot       0.1.0      2018-01-28 [1] CRAN (R 3.5.1)                  

@@

#> [1] /home/mturgeon/Rlibs
#> [2] /usr/local/lib/R/site-library
#> [3] /usr/lib/R/site-library
#> [4] /usr/lib/R/library

@@

\begin{CodeOutput}
#> Local:    Jesse-Islam-master /home/mturgeon/Documents/git_repositories/cbpaper
#> Head:     [71a5a9c] 2019-12-06: Lit-Review Edits
\end{CodeOutput}
\end{CodeChunk}
